\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Parimal N. Mahindrakar} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+(91) 9373739698 \\ Pune, Maharashtra, India} 
\address{\href{mailto:parimalm4653@gmail.com}{parimalm4653@gmail.com} \\ \href{https://www.linkedin.com/in/parimal-mahindrakar-189226190/}{LinkedIn} \\ \href{https://github.com/parimalmahindrakar}{GitHub}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{\textbf{Product Engineer - 1} with \textbf{one} year of experience in ROR development, seeking full time software development roles.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf B.E. in Information Technology}, Savitribai Phule Pune University \hfill {2018-2022}

{\bf Honors in Data Science}, Savitribai Phule Pune University \hfill {2020-2022}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & Python, Java, JavaScript, Ruby
\\
Frameworks & Flask, Django, RoR, NodeJS\\
Databases & MySQL, MongoDB\\
Version Conrtrol & Git, Github\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Product Engineer - 1 \textit{(Full Time)}} \hfill JUL 2022 - Present\\
K2V2 Technologies [\href{https://www.sell.do/}{sell.do}] \hfill \textit{Pune, India}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Working on several CRM product modules, such as sales, pre-sales, post-sales, inventory,reports, etc.
     \item Delivered almost 10 to 12 features for the system like, Refund after cancellation, Notifications for post sales, Default UI reports, disable inventory, disable post-sales functionalities.
    \item Spotted and removed various bugs, developed multiple reports for various clients.
    \item We have used Ruby and Backbone.js for back-end and front-end respectively.
 \end{itemize}
 
\textbf{Python and Web developer \textit{(Intern)}} \hfill OCT 2020-JAN 2021\\
InvestSaathi \hfill \textit{Banglore, India (Remote)}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Developed \href{https://finsuggest.com/}{finsuggest.com} static website using web designing tools. (NodeJS)
     \item Worked on NSE data through web scraping using Python (Standalone application)
 \end{itemize}

 \textbf{Python developer \textit{(Intern)}} \hfill JUN 2021-AUG 2021\\
\href{https://www.ust.com/}{UST Globals} \hfill \textit{Banglore, India (Remote)}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Worked on the ARCG (Auto Root Cause Generator) project.
     \item Generated the model which will differ the bugs based on their severity.
     \item Also created website as a tool in flask which will connect the model with UI.
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1em}
\item \textbf{Ecommerce Web Application (Django)} : {Developed a fully functional Ecommerce website using Django. I have worked on both the front-end and back-end. You can visit source code \href{https://github.com/parimalmahindrakar/DjangoEcommerce}{here}.}
\item \textbf{Customer Order Management (Flask)} : {To become familiar with the Flask framework and perform actual MySQL work. I created a website that will control how customers place their orders. You can view my source code \href{https://github.com/parimalmahindrakar/flask}{here} as well.}
\item \textbf{Construction Material Management (NodeJS)} : {Again to become familiar with NodeJS and perform actual MySQL work. In a group of 4 members we created a website that will control how clients will place their orders for the materials they require for the construction. You can view my source code right \href{https://github.com/parimalmahindrakar/flask}{here} as well.}
\end{rSection} 

%----------------------------------------------------------------------------------------

\end{document}
